External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-28 CVPR2017_Review_Unified.tex
add

\begin{figure*}\label{fig2}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (a) Noisy Image \\ (34.66dB/0.9178)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (h) Offline \\ (34.97dB/0.9441) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (i) Online \\ (36.86dB/0.9622) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (j) Guided \\ (\textbf{37.09}dB/\textbf{0.9638})}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

@@

\begin{figure*}\label{fig3}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

@@

Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$. For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$. We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Equ. (\ref{equ3})) to guide the learning of an orthogonal dictionary defined as $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$. This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$. Therefore, the dictionary $\mathbf{D}_{k}$ can adaptively characterize the internal PGs in the $k$-th subspace. For notation simplicity, we ignore the subspace index $k$ and denote the noisy PGs assigned to each subspace as $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$. The learning is performed under the weighted sparse coding framework proposed as follows:
\vspace{-2mm}
\begin{equation}\label{equ5}\vspace{-2mm}
\begin{split}
&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n,m}\}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|)
\\
&
\text{s.t.}
\quad
\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
where $\bm{\alpha}_{n,m}$ is the sparse coefficients vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$. $\lambda_{j}$ is the $j$-th regularization parameter defined as
\vspace{-2mm}
\begin{equation}\label{equ6}\vspace{-2mm}
\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
\end{equation}
We employ square roots of the singular values in $\mathbf{S}$ (please refer Equ. (\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator. Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-1mm}
\mathbf{D}^{\top}\mathbf{D} = 
\left[\begin{array}{c}
\mathbf{D}_{e}^{\top}
\\
\mathbf{D}_{i}^{\top}
\end{array}\right]
[\mathbf{D}_{e}\ \mathbf{D}_{i}]
=
\left[\begin{array}{cc}
\mathbf{D}_{e}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i}
\\
\mathbf{D}_{i}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i}
\end{array}\right]
=
\mathbf{I}
\end{equation}

Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ5}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}_{(0)}=\mathbf{U}_{k}$ and for $t=0, 1, ..., T-1$, alternatively do:
\\
\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficients via solving
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\begin{split}
&\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}_{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
\\
&
\text{s.t.}
\quad
\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
\vspace{-2mm}
\begin{equation}\label{equ9}\vspace{-2mm}
\bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
\\
\textbf{Updating Internal Orthogonal Dictionary}: given the sparse coefficients vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ10} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{i}}
\sum_{n=1}^{N}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{i}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
\text{s.t.}
\quad
\mathbf{D}
&
=
[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}$ and the internal part $\mathbf{A}_{i}^{(t)}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively. According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ10}) 
has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ11}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}
\end{equation}

@@

We evaluate the performance of the proposed framework on denoising real noisy images. The denoising is simultaneously done with the guided internal dictionary learning (DL) process. We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity. In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction. Until now, we obtain the solutions of sparse coefficients vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ. (\ref{equ10}). Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by 
\vspace{-2mm}
\begin{equation}\label{equ12}\vspace{-2mm}
\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
\end{equation}
where $n=1,...,N;m=1,...,M$.
\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Patch Group (PG) Prior Guided Internal
\\
\quad \quad \quad PG Prior Learning for Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $Ite = 1:IteNum$ \textbf{do}
\\
1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
\\
%\textbf{Guided Internal Subspace Selection:}
%\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
\\
\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Subspace selection via Equ. (\ref{equ4});
\\
\quad\textbf{end for}
\\
%\textbf{Guided Internal Orthogonal Dictionary Learning:}
%\\
\quad\textbf{for} the PGs in each Subspace \textbf{do}
\\
4.\quad External PG prior Guided Internal Orthogonal
\\
\quad \ \ \ Dictionary Learning by solving (\ref{equ5});
\\
5.\quad Recover each patch in all PGs via Equ. (\ref{equ12});
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}
The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.

>>>>

\begin{figure*}\label{fig2}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (a) Noisy Image \\ (34.66dB/0.9178)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (h) Offline \\ (34.97dB/0.9441) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (i) Online \\ (36.86dB/0.9622) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (j) Guided \\ (\textbf{37.09}dB/\textbf{0.9638})}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
\end{figure*}

@@

\begin{figure*}\label{fig3}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
\end{figure*}

@@

Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$. For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$. We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Equ. (\ref{equ3})) to guide the learning of an orthogonal dictionary for adaptively characterizing the internal PGs in the $k$-th subspace. The learned dictionary defined as $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$ has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$. For notation simplicity, we ignore the subspace index $k$ and denote the noisy PGs assigned to each subspace as $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$. The learning is performed under the weighted sparse coding framework proposed as follows:
\vspace{-2mm}
\begin{equation}\label{equ5}\vspace{-3mm}
\begin{split}
&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n,m}\}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|)
\\
&
\text{s.t.}
\quad
\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
where $\bm{\alpha}_{n,m}$ is the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$. $\lambda_{j}$ is the $j$-th regularization parameter defined as
\vspace{-1mm}
\begin{equation}\label{equ6}\vspace{-1mm}
\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
\end{equation}
We employ square roots of the singular values in $\mathbf{S}$ (please refer to Equ. (\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator. Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-1mm}
\mathbf{D}^{\top}\mathbf{D} = 
\left[\begin{array}{c}
\mathbf{D}_{e}^{\top}
\\
\mathbf{D}_{i}^{\top}
\end{array}\right]
[\mathbf{D}_{e}\ \mathbf{D}_{i}]
=
\left[\begin{array}{cc}
\mathbf{D}_{e}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i}
\\
\mathbf{D}_{i}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i}
\end{array}\right]
=
\mathbf{I}
\end{equation}

Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ5}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}_{(0)}=\mathbf{U}_{k}$ and for $t=0, 1, ..., T-1$, alternatively do:
\\
\textbf{Updating Sparse Coefficient}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ via solving
\vspace{-3mm}
\begin{equation}\label{equ8}\vspace{-3mm}
\begin{split}
&\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}_{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
\\
&
\text{s.t.}
\quad
\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
\vspace{-2mm}
\begin{equation}\label{equ9}\vspace{-2mm}
\bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
\\
\textbf{Updating Internal Dictionary}: given the sparse coefficient vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ10} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{i}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{i}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
\text{s.t.}
\quad
\mathbf{D}
&
=
[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively. According to the Theorem 4 in \cite{spca}, the problem (\ref{equ10}) 
has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times 3p^2}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ11}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}.
\end{equation}
The orthogonality of the dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
$(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.

@@

We evaluate the performance of the proposed framework on denoising real noisy images. The denoising is simultaneously done with the guided internal dictionary learning (DL) process. We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity. In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction. Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ. (\ref{equ10}). Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by 
\vspace{-2mm}
\begin{equation}\label{equ12}\vspace{-2mm}
\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
\end{equation}
where $n=1,...,N;m=1,...,M$.
\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Patch Group (PG) Prior Guided Internal
\\
\quad \quad \quad PG Prior Learning for Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $Ite = 1:IteNum$ \textbf{do}
\\
1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
\\
%\textbf{Guided Internal Subspace Selection:}
%\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
\\
\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Subspace selection via Equ. (\ref{equ4});
\\
\quad\textbf{end for}
\\
%\textbf{Guided Internal Orthogonal Dictionary Learning:}
%\\
\quad\textbf{for} the PGs in each Subspace \textbf{do}
\\
4.\quad External PG prior Guided Internal Orthogonal
\\
\quad \ \ \ Dictionary Learning by solving (\ref{equ5});
\\
5.\quad Recover each patch in all PGs via Equ. (\ref{equ12});
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}
The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.
